On Determinism of Game Engines used for Simulation-based Autonomous Vehicle Verification

### 2021-04-20 document/arxiv/det_arxiv.tex
rename top level files, fixed oreilly ref error
acknowledgements
single corresponding author

\maketitle
\let\thefootnote\relax\footnotetext{\textit{Greg Chance and Abanoub Ghobrial contributed equally to this paper and are both corresponding authors.}
Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom. 
%
S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England, Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.}
\makeatletter
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
                       {-18\p@ \@plus -4\p@ \@minus -4\p@}%
                       {4\p@ \@plus 2\p@ \@minus 2\p@}%
                       {\normalfont\normalsize\bfseries\boldmath
                        \rightskip=\z@ \@plus 8em\pretolerance=10000 }}
\makeatother

@@

% ***************************************************
%  Thanks
% ***************************************************
\section*{Acknowledgement}
This research has in part been funded by the ROBOPILOT and CAPRI projects. Both projects are part-funded by the Centre for Connected and Autonomous Vehicles (CCAV), delivered in partnership with Innovate UK under grant numbers 103703 (CAPRI) and 103288 (ROBOPILOT), respectively.
%
\textit{Greg Chance and Abanoub Ghobrial contributed equally to this paper.}
\balance

>>>>

\maketitle
\let\thefootnote\relax\footnotetext{\textit{Greg Chance and Abanoub Ghobrial contributed equally to this paper, Greg Chance is the corresponding author.}
Greg Chance (e-mail: greg.chance@bristol.ac.uk), 
Abanoub Ghobrial (e-mail: abanoub.ghobrial@bristol.ac.uk), 
Kevin McAreavey (e-mail: kevin.mcareavey@bristol.ac.uk), 
and 
Kerstin Eder (e-mail: kerstin.eder@bristol.ac.uk) 
are with the Trustworthy Systems Lab, Department of Computer Science, University of Bristol, Merchant Ventures Building, Woodland Road,  Bristol, BS8 1UQ, United Kingdom. 
%
S\'everin Lemaignan (e-mail: severin.lemaignan@brl.ac.uk)
and
Tony Pipe (e-mail: tony.pipe@brl.ac.uk), 
are with the Bristol Robotics Lab, T Block, University of the West of England, Frenchay, Coldharbour Ln, Bristol, BS34 8QZ, United Kingdom.}
\makeatletter
\renewcommand\subsubsection{\@startsection{subsubsection}{3}{\z@}%
                       {-18\p@ \@plus -4\p@ \@minus -4\p@}%
                       {4\p@ \@plus 2\p@ \@minus 2\p@}%
                       {\normalfont\normalsize\bfseries\boldmath
                        \rightskip=\z@ \@plus 8em\pretolerance=10000 }}
\makeatother

@@

\balance
